Meta-analysis

### 2020-01-16 05_MetaAnalysis.Rmd
Remove lmer analysis of "slim" data

```{r MEsummary_Libraries, message=FALSE}
# install.packages("tidyverse")
# install.packages("devtools")
# devtools::install_github("https://github.com/PaulMelloy/bomrang")
# devtools::install_github("https://github.com/adamhsparks/theme.usq")
# install.packages("lme4")

library(RColorBrewer)
library(tidyverse)
library(theme.usq)
library(bomrang)
library(lme4)
library(kableExtra)

@@

Now for the trickier part creating 'Sampling Variance' for treatments where only mean yield is recorded.  
The trial which does not report any type of variance also reports that there is no significant difference between the means.

```{r}
NATrials <- PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole",
          row_spacing == 0.75,
          is.na(Y_error_type)) %>%
   select(trial_ref) %>%
   distinct()
```

A single trial `mung1516/03` within the current scope of the meta-analysis fails to report a variance statistic. According to [Machado F. et. al (2017)](http://apsjournals.apsnet.org/doi/10.1094/PDIS-03-17-0340-RE) [Paul et al. (2007)](https://apsjournals.apsnet.org/doi/pdfplus/10.1094/PHYTO-97-2-0211) uses linear regression model to estimate sampling variance.

@@

```{r slim_lmer}
slim_PM_dat <- read.csv("data/slim_PM_clusterdat.csv")

m4 <- lmer(grain_yield.t.ha*1000 ~ factor(spray_management) + (factor(spray_management) | trial_ref), data = slim_PM_dat)

m5 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) + (factor(spray_management) | trial_ref), data = slim_PM_dat)

m5.0 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) + (1 | trial_ref), data = slim_PM_dat)

anova(m4,m5) # m5 has a much lower AIC and significantly better model
anova(m5,m5.0) # no difference
```

Model 5 (m5) is a significantly better fit than model 4 (m4). Model 5.0 (m5.0), a simpler model with less variables, was not significantly different from m5. This analyis suggests that model 5.0 is the best fit.
`r summary(m5.0)`

```{r LME_cluster_disease_mod}
m6 <- lmer(grain_yield.t.ha*1000 ~ factor(spray_management) * PM_final_severity +
              (factor(spray_management) | trial_ref), 
           data = slim_PM_dat)

m7 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) * PM_final_severity + 
              (factor(spray_management) | trial_ref), 
           data = slim_PM_dat)

anova(m5,m6) # 65 has a lower AIC but not evaluated as a significantly better model

summary(m6)

```{r LME_slimmer_cluster_disease_mod}
library(lme4)
slimmer_PM_dat <- read.csv("data/slimmer_PM_clusterdat.csv")
unique(slimmer_PM_dat$trial_ref, slimmer_PM_dat$location, slimmer_PM_dat$year)

@@

anova(m8,m9) # m9 is significantly better model
anova(m9,m10) # m9 is significantly better model

>>>>

```{r MEsummary_Libraries, message=FALSE}
# install.packages("tidyverse")
# install.packages("devtools")
# devtools::install_github("https://github.com/PaulMelloy/bomrang")
devtools::install_github("https://github.com/adamhsparks/theme.usq", dependencies = TRUE)
# install.packages("lme4")

library(RColorBrewer)
library(tidyverse)
library(theme.usq)
library(bomrang)
library(lme4)
library(kableExtra)
```

@@

Now for the tricy part creating 'Sampling Variance' for treatments where only mean yield is recorded.  
The trial which does not report any type of variance also reports that there is no significant difference between the means.

```{r NAtrials}
NATrials <- PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole",
          row_spacing == 0.75,
          is.na(Y_error_type)) %>%
   select(trial_ref) %>%
   distinct()
```

Two trials `mung1516/03` and `mung1112/01` within the scope of the meta-analysis fail to report variance statistics. According to [Machado F. et. al (2017)](http://apsjournals.apsnet.org/doi/10.1094/PDIS-03-17-0340-RE) [Paul et al. (2007)](https://apsjournals.apsnet.org/doi/pdfplus/10.1094/PHYTO-97-2-0211) we can use a linear regression model to estimate sampling variance.

@@

```{r LME_slimmer_cluster_disease_mod}
library(lme4)
slimmer_PM_dat <- read.csv("data/slimmer_PM_clusterdat.csv")

@@

m11 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) + 
              (1 | trial_ref), 
           data = slimmer_PM_dat)

anova(m8,m9) # m9 is significantly better model
anova(m9,m10) # m9 is significantly better model
anova(m9,m11) # m11 is a simpler model which is no different to m9
